Dirac neutrino mass generation from Majorana messenger

### 2019-09-18 draft.tex
pt

\begin{abstract}    
  The radiative type-I seesaw have been already implemented to explain the lightness of Majorana neutrinos with both Majorana and Dirac heavy fermions, and the lightness of Dirac    neutrinos with                   Dirac heavy fermions. In this work we present a minimal implementation of the radiative type-I seesaw with light Dirac neutrinos and heavy Majorana fermions. An inert doublet and a complex singlet scalar complete the dark sector which is protected by an Abelian fermiophobic gauge symmetry that also forbids three level mass contributions for the full set of light neutrinos. A fermion vector-like extension of the model is also proposed where the light right-handed neutrinos can thermalize in the primordial plasma and the extra gauge boson can be directly produced at colliders. ...
%some results here
  This model is restricted by  neutrino physics,  lepton flavor violation and cosmological constrains, including  
the effective number light neutrinos $N_{\text{eff}}$. Here we find that $M_{Z^{\prime}}/g^{\prime} \gtrsim 40\ \text{TeV}$ in order to satisfy the conditions of $N_{\text{eff}}$..
\end{abstract}

@@

In view of this we have proposed a new mechanism for Dirac neutrino masses which making use of heavy Majorana mediators generate nonzero masses at one-loop level. 
The model presented in this paper is a one-loop realization of the dimension 6 operator $\overline{L} \tilde{H} \nu_R S^2\,$ and enters into the list of Dirac radiative type-I seesaw models with the novel feature that it involves Majorana mediators rather Dirac mediators. 
The Diracness of the massive neutrinos is protected by only one extra $\operatorname{U}(1)_X$ gauge symmetry, which in turn ensures the stability of the lightest particle mediating the one-loop neutrino mass diagram. 
In this way the model offers in a non trivial way a the solution to both neutrino and DM puzzles.
Moreover, we have shown that going beyond the minimal model other interesting phenomenological aspects arise such that possible signals at colliders and new contributions to the number of extra relativistic species. In particular, the  current upper bound on $\Delta N_{\text{eff}}$ reported by PLANCK points to large ratios $M_{Z'}\gtrsim 40\ \text{TeV}$. Future cosmic microwave background experiments may probe all the no minimal models presented here.

>>>>

\begin{abstract}    
  The radiative type-I seesaw have been already implemented to explain the lightness of Majorana neutrinos with both Majorana and Dirac heavy fermions, and the lightness of Dirac    neutrinos with                   Dirac heavy fermions. In this work we present a minimal implementation of the radiative type-I seesaw with light Dirac neutrinos and heavy Majorana fermions. An inert doublet and a complex singlet scalar complete the dark sector which is protected by an Abelian fermiophobic gauge symmetry that also forbids three level mass contributions for the full set of light neutrinos. A fermion vector-like extension of the model is also proposed where the light right-handed neutrinos can thermalize in the primordial plasma and the extra gauge boson can be directly produced at colliders.
In particular, the  current upper bound on $\Delta N_{\text{eff}}$ reported by PLANCK points to large ratios $M_{Z'}/g'\gtrsim 40\ \text{TeV}$, while future cosmic microwave background experiments may probe all the no minimal models presented here. 
\end{abstract}

@@

In view of this we have proposed a new mechanism for Dirac neutrino masses which making use of heavy Majorana mediators generate nonzero masses at one-loop level. 
The model presented in this paper is a one-loop realization of the dimension 6 operator $\overline{L} \tilde{H} \nu_R S^2\,$ and enters into the list of Dirac radiative type-I seesaw models with the novel feature that it involves Majorana mediators rather Dirac mediators. 
The Diracness of the massive neutrinos is protected by only one extra $\operatorname{U}(1)_X$ gauge symmetry, which in turn ensures the stability of the lightest particle mediating the one-loop neutrino mass diagram. 
In this way the model offers in a non trivial way a the solution to both neutrino and DM puzzles.
Moreover, we have shown that going beyond the minimal model other interesting phenomenological aspects arise such that possible signals at colliders and new contributions to the number of extra relativistic species. In particular, the  current upper bound on $\Delta N_{\text{eff}}$ reported by PLANCK points to large ratios $M_{Z'}/g'\gtrsim 40\ \text{TeV}$. Future cosmic microwave background experiments may probe all the no minimal models presented here.
